
```{r title, include = FALSE}
front_title <- "RDBES CL CE National overview"
```

<!-- The output directory below defines the path the html file will be saved at -->

---
title: `r front_title`
date: "`r format(Sys.time(), '%d %B, %Y')`"
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_file = paste0(substr(inputFile,1,nchar(inputFile)-4),".html"), 
  output_dir = "H:/RDBES")})
output:
  html_document
fontsize: 12pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
options(scipen=999)
```

```{r libraries}
library(tidyverse)
library(knitr)
library(kableExtra)
library(ggplot2)
library(mapplots)
library(rnaturalearth)
library(rnaturalearthdata)
library(sf)
library(DT)
library(stringr)
```

```{r functions}
catHeader <- function(text = "", level = 3) {
    cat(paste0("\n\n", 
               paste(rep("#", level), collapse = ""), 
               " ", text, "\n"))
}
```

```{r source}
#Read the rectangle list from the repository 
url <- "https://github.com/ices-tools-dev/RDBES/raw/master/QC-scripts/RectangleList/ICESRectAreas.csv"
ICESrect <- read.csv(url, header = TRUE)
urls <- "https://github.com/ices-tools-dev/RDBES/raw/master/QC-scripts/SpeciesScientificName/ICESVocabAphiaIDScienName.csv"
ScienName <- read.csv(urls, header = TRUE)

# Remove deprecated and invalid records 
ScienName <- filter(ScienName, !Deprecated %in% c("", "True", "2020-09-16")) %>%
  select(Code, Description) %>%
  mutate(Code = as.numeric(Code))

```

```{r data}
# Read test data 
CL <- read.csv("./ZW_1965_HCL.csv")
CE <- read.csv("./ZW_1965_HCE.csv")

#--Give the df's the R column names from the RDBES data model CL CE file
 
CLnames <- c("CLrecType", "CLdTypSciWeig", "CLdSouSciWeig", "CLsampScheme", "CLdSouLanVal", "CLlanCou", "CLvesFlagCou", "CLyear", "CLquar", "CLmonth", "CLarea", "CLstatRect", "CLgsaSubarea", "CLjurisdArea", "CLeconZoneIndi", "CLspecCode", "CLspecFAO", "CLlandCat", "CLcatchCat", "CLregDisCat","CLsizeCatScale", "CLsizeCat", "CLnatFishAct", "CLmetier6", "CLIBmitiDev", "CLloc", "CLvesLenCat", "CLfishTech", "CLdeepSeaReg", "CLoffWeight", "CLsciWeight", "CLexpDiff", "CLtotOffLanVal", "CLnumUniqVes", "CLsciWeightRSE", "CLvalRSE", "CLsciWeightQualBias")

colnames(CL) <- CLnames

CEnames <- c("CErecType", "CEdTypSciEff", "CEdSouSciEff", "CEsampScheme", "CEvesFlagCou", "CEyear", "CEquar", "CEMonth", "CEArea", "CEstatRect", "CEgsaSubarea", "CEjurisdArea", "CEeconZoneIndi", "CEnatFishAct", "CEmetier6", "CEIBmitiDev", "CEloc", "CEvesLenCat", "CEfishTech", "CEdeepSeaReg", "CEnumFracTrips", "CEnumDomTrip", "CEoffDaySea", "CESciDaySea", "CEoffFishDay", "CEsciFishDay", "CEoffNumHaulSet", "CEsciNumHaulSet", "CEoffVesFishHour", "CEsciVesFishHour", "CEoffSoakMeterHour", "CEsciSoakMeterHour", "CEoffkWDaySea", "CEscikWDaySea", "CEoffkWFishDay", "CEscikWFishDay", "CEoffkWFishHour", "CEscikWFishHour", "CEgTDaySea", "CEgTFishDay", "CEgTFishHour", "CEnumUniqVes", "CEsciFishDayRSE", "CEscientificFishingDaysQualBias")

colnames(CE) <- CEnames
```

```{r changeIDtoSC}
# Choice of Aphiad ID or Scientific name (from ICES Vocab)
# Default is TRUE - If FALSE the AphiaID is used

ScName <- TRUE

if(ScName %in% TRUE){
  CL <- left_join(CL, ScienName, by = c("CLspecCode" = "Code")) %>%
    rename(CLSpecies = Description) #generic field name for the code to work regardless of aphiaID or scientific name
}else{
  CL <- rename(CL, CLSpecies = CLspecCode)
}
```

```{r CLCEcon}
CL$CLSpecies[CL$CLSpecies==''] <- as.character(CL$CLSpecies)
CL$CLyear <- as.character(CL$CLyear)
CE$CEyear <- as.character(CE$CEyear)

# Month factors 
CL$CLmonth <- factor(CL$CLmonth, levels = as.character(c(1:12)))
CE$CEMonth <- factor(CE$CEMonth, levels = as.character(c(1:12)))

# Vessel length factors 
CL$CLvesLenCat <- factor(CL$CLvesLenCat, levels = c("<8", "8-<10", "10-<12", "12-<15", "15-<18", "18-<24", "24-<40", "40<", "Unknown"))
CE$CEvesLenCat <- factor(CE$CEvesLenCat, levels = c("<8", "8-<10", "10-<12", "12-<15", "15-<18", "18-<24", "24-<40", "40<", "Unknown"))

# Get gear for passive/active
CE <- mutate(CE, CEGear = str_extract(CEmetier6, "[^_]+"))
CE <- mutate(CE, CEGearActivity = ifelse(CEGear %in% c("FIX", "FAR", "FPN", "FPO", "FWR", "FYK", "GEN", "GNF", "GN", "GNC", "GND", "GNS", "GTN", "GTR", "GES", "LH", "LHM", "LHP", "LL", "LLD", "LLF", "LLS", "LTL", "LVD", "LVS", "LX", "LN", "LNB", "LNP", "LNS","MIS"), "Passive", ifelse(CEGear %in% "NK", "NK", "Active")))
```



```{r topMet}
#Find top 20 CLSpecies
top20_CLSpecies <- CL %>%
  group_by(CLSpecies) %>%
  summarise(lwTot=sum(CLtotOffLanVal)) %>%
  arrange(desc(lwTot)) %>%
  top_n(20)
top20_CLSpecies$Top20CLSpecies <- "X"
CL1 <- left_join(CL,top20_CLSpecies,by="CLSpecies")
CL1$topCLSpecies <- ifelse(is.na(CL1$Top20CLSpecies),"OTH",CL1$CLSpecies)

#Find top 20 metiers
top20_metiers <- CL1 %>%
  group_by(CLmetier6) %>%
  summarise(lwTot=sum(CLtotOffLanVal)) %>%
  arrange(desc(lwTot)) %>%
  top_n(20)
top20_metiers$Top20metiers <- "X"
CL1 <- left_join(CL1,top20_metiers,by="CLmetier6")
CL1$topMetiers <- ifelse(is.na(CL1$Top20metiers),"OTH",CL1$CLmetier6)

```


## CL table (top 20 species (rest grouped in OTH group)) {.tabset}

### CL weight by year and month

```{r CLweightYear, fig.dim= c(12, 8)}
CLweightYear <- CL1 %>%
  group_by(CLyear, CLmonth) %>%
  summarise(CLsciWeight = sum(CLsciWeight)) 

ggplot(CLweightYear, aes(CLmonth, CLsciWeight, fill=CLyear)) +
  geom_bar(position="dodge", stat="identity") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.key.size = unit(2, 'cm'))  +
  xlab("CLMonth") +
  labs(fill = "CLyear")

```


### CL official weight vs scientific weight 

```{r CLoffweightSciweightSP, fig.dim= c(12, 8)}
CLweightS <- CL1 %>%
  group_by(topCLSpecies) %>%
  summarise(CLoffWeight = sum(CLoffWeight),
            CLsciWeight = sum(CLsciWeight)) %>%
  gather(CLweightSource, CLweight, -c(topCLSpecies))


ggplot(CLweightS, aes(reorder(topCLSpecies, -CLweight), CLweight, fill = CLweightSource)) +
  geom_bar(position="dodge", stat="identity") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.key.size = unit(2, 'cm'))+
  xlab("topCLSpecies")

```


### CL scientific weight source

```{r CLoffweightSciweightSourceSP, fig.dim= c(12, 8)}
CLweightSource <- CL1 %>%
  group_by(topCLSpecies, CLdSouSciWeig) %>%
  summarise(CLsciWeight = sum(CLsciWeight)) 

ggplot(CLweightSource, aes(reorder(topCLSpecies, -CLsciWeight), CLsciWeight, fill = CLdSouSciWeig)) +
  geom_bar(position="stack", stat="identity") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.key.size = unit(2, 'cm')) +
  xlab("topCLSpecies")

```

### CL Landings by area (stacked)

```{r CLLanSArea, , fig.dim= c(12, 8)}
CLLanSArea <- CL1 %>%
  group_by(topCLSpecies, CLarea) %>%
  summarise(CLoffWeight = sum(CLoffWeight))

CLLanSArea <- CLLanSArea %>%
  group_by(topCLSpecies) %>%
  mutate(TotW = sum(CLoffWeight))

ggplot(CLLanSArea, aes(reorder(topCLSpecies, -TotW), CLoffWeight, fill = CLarea)) +
  geom_bar(position="stack", stat="identity") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  xlab("topCLSpecies")
```


### CL Landings value source 

```{r CLValSSP, fig.dim= c(12, 8)}
CLValS <- CL1 %>%
  group_by(topCLSpecies, CLdSouLanVal) %>%
  summarise(CLoffWeight = sum(CLoffWeight)) 

ggplot(CLValS, aes(reorder(topCLSpecies, -CLoffWeight), CLoffWeight, fill = CLdSouLanVal)) +
  geom_bar(position="stack", stat="identity") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.key.size = unit(2, 'cm')) +
  xlab("topCLSpecies")
```

### CL Landing category 

```{r CLlandCatSP, fig.dim= c(12, 8)}
CLValS2 <- CL1 %>%
  group_by(topCLSpecies, CLlandCat) %>%
  summarise(CLoffWeight = sum(CLoffWeight))

ggplot(CLValS2, aes(reorder(topCLSpecies, -CLoffWeight), CLoffWeight, fill = CLlandCat)) +
  geom_bar(position="stack", stat="identity") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.key.size = unit(2, 'cm')) +
  xlab("topCLSpecies")
```

### CL Catch category 

```{r CLcatchCatSP, fig.dim= c(12, 8)}

CLValS3 <- CL1 %>%
  group_by(topCLSpecies,CLcatchCat) %>%
  summarise(CLoffWeight = sum(CLoffWeight))

ggplot(CLValS3, aes(reorder(topCLSpecies, -CLoffWeight), CLoffWeight, fill = CLcatchCat)) +
  geom_bar(position="stack", stat="identity") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.key.size = unit(2, 'cm')) +
  xlab("topCLSpecies")
```

## CL official weight by area {.tabset}

```{r  CLoffWeight1SP}

CLWeightG <- CL1 %>%
  group_by(topCLSpecies, CLarea, CLyear) %>%
  summarise(CLoffWeight = sum(CLoffWeight))

myplots <- list()
for(i in unique(CLWeightG$topCLSpecies)){
  myplots[[i]] <- 
    ggplot(subset(CLWeightG, topCLSpecies == i), aes(reorder(CLarea, -CLoffWeight), CLoffWeight, fill = as.character(CLyear)))+
    geom_bar(position="stack",stat = "identity") +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.key.size = unit(2, 'cm'))  +
    xlab("CLarea") +
    labs(fill = "CLyear")
}
```

```{r CLoffWeightplot1SP, results = "asis", fig.dim= c(12, 8)}

for(i in unique(names(myplots))){
    # The tabset level here has to be lower than the
    # parent level (ie, parent is 2, so here you have to use 3)
    catHeader(names(myplots[i]), 3)
    lapply(myplots[i], print)
}
```


## CL official weight by vessel length category {.tabset}

```{r  CLoffWeightVelSP}

CLVel <- CL1 %>%
  group_by(topCLSpecies, CLarea,CLvesLenCat) %>%
  summarise(CLoffWeight = sum(CLoffWeight)) 


CLVel <- CLVel %>%
  group_by(CLarea, topCLSpecies) %>%
  mutate(TotW = sum(CLoffWeight))

myplotsVel <- list()
for(i in unique(CLVel$topCLSpecies)){
  myplotsVel[[i]] <- 
    ggplot(subset(CLVel, topCLSpecies == i), aes(reorder(CLarea, -TotW), CLoffWeight, fill = CLvesLenCat)) +
  geom_bar(stat = "identity") +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    xlab("CLarea")
}
```

```{r CLoffWeightVelplotSP, results = "asis", fig.dim= c(12, 8)}

for(i in unique(names(myplotsVel))){
    catHeader(names(myplotsVel[i]), 3)
    lapply(myplotsVel[i], print)
}

```


## CL official weight vs total official landings value {.tabset}

```{r  CLoffWeightValSP}

myplotsVal <- list()
for(i in sort(unique(CL1$topCLSpecies))){
  myplotsVal[[i]] <- 
    ggplot(subset(CL1, topCLSpecies == i), aes(x= CLoffWeight, y=CLtotOffLanVal)) + geom_point()
}
```

```{r CLoffWeightValplotSP, results = "asis"}

for(i in unique(names(myplotsVal))){
    catHeader(names(myplotsVal[i]), 3)
    lapply(myplotsVal[i], print)
}
```



## CL Landing location {.tabset}

```{r  CLoffWeightLoc}

CLLoc <- CL1 %>%
  group_by(topCLSpecies, CLarea, CLloc) %>%
  summarise(CLoffWeight = sum(CLoffWeight))

CLLoc <- CLLoc %>%
  group_by(CLarea, topCLSpecies) %>%
  mutate(TotW = sum(CLoffWeight))

myplotsLoc <- list()
for(i in unique(CLLoc$topCLSpecies)){
  myplotsLoc[[i]] <- 
    ggplot(subset(CLLoc, topCLSpecies == i), aes(reorder(CLarea, -TotW), CLoffWeight, fill = CLloc)) +
    geom_bar(stat = "identity") +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    xlab("CLarea")
}
```

```{r CLoffWeightLocplot, results = "asis", fig.dim= c(12, 8)}

for(i in unique(names(myplotsLoc))){
    catHeader(names(myplotsLoc[i]), 3)
    lapply(myplotsLoc[i], print)
}
```


## CL top 20 species maps {.tabset}


```{r  CLMapSP}

world <- ne_countries(scale = "medium", returnclass = "sf")
world <- st_set_crs(world, 4326)

CLMap <- CL1 %>%
  distinct(CLstatRect, topCLSpecies) %>%
  mutate(lon = ices.rect(CLstatRect)$lon,
         lat = ices.rect(CLstatRect)$lat)
 

myplotsMap <- list()
for(i in sort(unique(CLMap$topCLSpecies))){
  min.lon<-min(CLMap$lon, na.rm = T)
  max.lon<-max(CLMap$lon, na.rm = T)
  min.lat<-min(CLMap$lat, na.rm = T)
  max.lat<-max(CLMap$lat, na.rm = T)
  myplotsMap[[i]] <- 
    ggplot() +
    theme_bw() +
    geom_sf(data=world)+
    geom_point(data = subset(CLMap, topCLSpecies == i), aes(lon, lat), size=2, colour="red") +
    coord_sf(xlim = c(min.lon, max.lon), ylim = c(min.lat, max.lat)) +
    xlab("Longitude") +
    ylab("Latitude")
}
```

```{r CLMapplot, results = "asis", fig.dim = c(12, 12)}

for(i in unique(names(myplotsMap))){
    catHeader(names(myplotsMap[i]), 3)
    lapply(myplotsMap[i], print)
}
```


## CL top 20 metiers (rest grouped in OTH group)) {.tabset}

### CL official weight vs scientific weight 

```{r CLoffweightSciweightME, fig.dim= c(12, 8)}
CLweightS <- CL1 %>%
  group_by(topMetiers) %>%
  summarise(CLoffWeight = sum(CLoffWeight),
            CLsciWeight = sum(CLsciWeight)) %>%
  gather(CLweightSource, CLweight, -c(topMetiers))

ggplot(CLweightS, aes(reorder(topMetiers, -CLweight), CLweight, fill = CLweightSource)) +
  geom_bar(position="dodge", stat="identity") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.key.size = unit(2, 'cm')) +
  xlab("topMetiers")

```


### CL scientific weight source

```{r CLoffweightSciweightSourceME, fig.dim= c(12, 8)}
CLweightSource <- CL1 %>%
  group_by(topMetiers, CLdSouSciWeig) %>%
  summarise(CLsciWeight = sum(CLsciWeight)) 

ggplot(CLweightSource, aes(reorder(topMetiers, -CLsciWeight), CLsciWeight, fill = CLdSouSciWeig)) +
  geom_bar(position="stack", stat="identity") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.key.size = unit(2, 'cm')) +
  xlab("topMetiers")

```

### CL Landings value source 

```{r CLValSME, fig.dim= c(12, 8)}

CLValS <- CL1 %>%
  group_by(topMetiers, CLarea,CLdSouLanVal) %>%
  summarise(CLoffWeight = sum(CLoffWeight))

ggplot(subset(CLValS), aes(reorder(topMetiers, -CLoffWeight), CLoffWeight, fill = CLdSouLanVal)) +
  geom_bar(position="stack", stat="identity") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.key.size = unit(2, 'cm')) +
  xlab("topMetiers")

```


## CL official weight by area {.tabset}

```{r  CLoffWeight1ME}

CLWeightG <- CL1 %>%
  group_by(topMetiers, CLarea, CLyear) %>%
  summarise(CLoffWeight = sum(CLoffWeight))

myplots <- list()
for(i in unique(CLWeightG$topMetiers)){
  myplots[[i]] <- 
    ggplot(subset(CLWeightG, topMetiers == i), aes(reorder(CLarea, -CLoffWeight), CLoffWeight, fill = CLyear))+
    geom_bar(stat = "identity") +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    xlab("CLarea")
}
```

```{r CLoffWeightplot1ME, results = "asis", fig.dim= c(12, 8)}

for(i in unique(names(myplots))){
    # The tabset level here has to be lower than the
    # parent level (ie, parent is 2, so here you have to use 3)
    catHeader(names(myplots[i]), 3)
    lapply(myplots[i], print)
}
```


## CL official weight by vessel length category {.tabset}

```{r  CLoffWeightVelME}

CLVel <- CL1 %>%
  group_by(topMetiers, CLarea,CLvesLenCat) %>%
  summarise(CLoffWeight = sum(CLoffWeight))

myplotsVel <- list()
for(i in unique(CLVel$topMetiers)){
  myplotsVel[[i]] <- 
    ggplot(subset(CLVel, topMetiers == i), aes(reorder(CLarea, -CLoffWeight), CLoffWeight, fill = CLvesLenCat)) +
  geom_bar(stat = "identity") +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.key.size = unit(2, 'cm')) +
    xlab("CLarea")
}
```

```{r CLoffWeightVelplotME, results = "asis", fig.dim= c(12, 8)}

for(i in unique(names(myplotsVel))){
    catHeader(names(myplotsVel[i]), 3)
    lapply(myplotsVel[i], print)
}
```


## CL top 20 metiers maps {.tabset}

```{r  CLMapME}

world <- ne_countries(scale = "medium", returnclass = "sf")
world <- st_set_crs(world, 4326)

CLMap <- CL1 %>%
  distinct(CLstatRect, topMetiers) %>%
  mutate(lon = ices.rect(CLstatRect)$lon,
         lat = ices.rect(CLstatRect)$lat)
 

myplotsMap <- list()
for(i in sort(unique(CLMap$topMetiers))){
  min.lon<-min(CLMap$lon, na.rm = T)
  max.lon<-max(CLMap$lon, na.rm = T)
  min.lat<-min(CLMap$lat, na.rm = T)
  max.lat<-max(CLMap$lat, na.rm = T)
  myplotsMap[[i]] <- 
    ggplot() +
    theme_bw() +
    geom_sf(data=world)+
    geom_point(data = subset(CLMap, topMetiers == i), aes(lon, lat), size=2, colour="red") +
    coord_sf(xlim = c(min.lon, max.lon), ylim = c(min.lat, max.lat)) +
    xlab("Longitude") +
    ylab("Latitude")
}
```

```{r CLMapplotME, results = "asis", fig.dim = c(12, 12)}

for(i in unique(names(myplotsMap))){
    catHeader(names(myplotsMap[i]), 3)
    lapply(myplotsMap[i], print)
}
```



## CL Potential Errors {.tabset}

### CL ICES rectangles and FAO Areas

Area and ICES rectangle in the CL data (AreaCLtable,RectangleCLtable) set is compared with area/rectangle relationship ICES reference list. 
The expected area related to the ICES rectangle is found in the column ICESAreaWithRectangle.
Note that -9 is allowed as unknown ICES rectangle.

```{r CLrectangles}
CLRect <- left_join(CL, ICESrect, by = c("CLstatRect" = "ICESNAME"))%>%
  select(CLarea, CLstatRect, Area) %>%
  distinct()

CLRectErr <- CLRect %>%
  group_by(CLstatRect) %>%
  summarise(CLarea = unique(CLarea),
            Area = paste0(unique(Area), collapse = ", ")) %>%
  rowwise() %>%
  mutate(NoMatch = grepl(CLarea, Area)) %>%
  filter(NoMatch %in% FALSE) %>%
  rename(ICESArea = Area) %>%
  ungroup() %>%
  select(CLstatRect, CLarea, ICESArea) %>%
  rename(RectangleCLtable = CLstatRect,
         AreaCLtable = CLarea,
         ICESAreaWithRectangle = ICESArea)

datatable(CLRectErr) 
```

## CE table 

## CE official effort vs scientific effort {.tabset}

### CL weight by year and month


```{r CEeffortYear, fig.dim= c(12, 8)}
CEDASYear <- CE %>%
  group_by(CEyear, CEMonth) %>%
  summarise(CESciDaySea = sum(CESciDaySea)) 

ggplot(CEDASYear, aes(CEMonth, CESciDaySea, fill=CEyear)) +
  geom_bar(position="dodge", stat="identity") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.key.size = unit(2, 'cm')) 

```

### Official days at sea vs scientific days at sea

```{r CLeffortDATS, fig.dim= c(12, 8)}
CEeffortDATS <- CE %>%
  group_by(CEArea) %>%
  summarise(CEoffDaySea = sum(CEoffDaySea),
            CESciDaySea = sum(CESciDaySea))  %>%
  gather(CEDaySeaSource, CEDaySea, -c(CEArea))

ggplot(CEeffortDATS, aes(reorder(CEArea, -CEDaySea), CEDaySea, fill = CEDaySeaSource)) +
  geom_bar(position="dodge", stat="identity") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.key.size = unit(2, 'cm')) +
  xlab("CEDaySea")

```


### Official days at sea and scientific days at sea (passive/active gears) 

```{r CLeffortDATSpa, fig.dim= c(12, 8)}
CEeffortDATSpa <- CE %>%
  group_by(CEArea, CEGearActivity) %>%
  summarise(CEoffDaySea = sum(CEoffDaySea),
            CESciDaySea = sum(CESciDaySea))  %>%
  gather(CEDaySeaSource, CEDaySea, -c(CEArea, CEGearActivity))

CEeffortDATSpa <- CEeffortDATSpa %>%
  group_by(CEArea) %>%
  mutate(TotE = sum(CEDaySea))

ggplot(CEeffortDATSpa, aes(reorder(CEArea, -TotE), CEDaySea, fill = CEGearActivity)) +
  geom_bar(position="stack", stat="identity") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.key.size = unit(2, 'cm')) +
  facet_grid(CEDaySeaSource~., scales = "free") +
  xlab("CEFishDay")
```

### Official fishing days vs scientific fishing days 

```{r CLeffortFDS, fig.dim= c(12, 8)}
CEeffortFDS <- CE %>%
  group_by(CEArea) %>%
  summarise(CEoffFishDay = sum(CEoffFishDay),
            CEsciFishDay = sum(CEsciFishDay))  %>%
  gather(CEFishDaySource, CEFishDay, -c(CEArea))

ggplot(CEeffortFDS, aes(reorder(CEArea, -CEFishDay), CEFishDay, fill = CEFishDaySource)) +
  geom_bar(position="dodge", stat="identity") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.key.size = unit(2, 'cm')) +
  xlab("CEFishDay")

```


### Official fishing days and scientific fishing days (passive/active gears) 

```{r CLeffortFDSpa, fig.dim= c(12, 8)}
CEeffortFDSpa <- CE %>%
  group_by(CEArea, CEGearActivity) %>%
  summarise(CEoffFishDay = sum(CEoffFishDay),
            CEsciFishDay = sum(CEsciFishDay))  %>%
  gather(CEFishDaySource, CEFishDay, -c(CEArea, CEGearActivity))

CEeffortFDSpa <- CEeffortFDSpa %>%
  group_by(CEArea) %>%
  mutate(TotE = sum(CEFishDay))

ggplot(CEeffortFDSpa, aes(reorder(CEArea, -TotE), CEFishDay, fill = CEGearActivity)) +
  geom_bar(position="stack", stat="identity") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.key.size = unit(2, 'cm')) +
  facet_grid(CEFishDaySource~., scales = "free") +
  xlab("CEFishDay")
```


### CE scientific effort source 

```{r CESciEffortSource, fig.dim= c(12, 8)}
CESciEffortSource <- CE %>%
  group_by(CEArea, CEdSouSciEff) %>%
  summarise(CESciDaySea = sum(CESciDaySea),
            CEsciFishDay = sum(CEsciFishDay)) %>%
  gather(CEEffSource, CEEffort, -c(CEArea, CEdSouSciEff)) 

ggplot(CESciEffortSource, aes(reorder(CEArea, -CEEffort), CEEffort, fill = CEdSouSciEff)) +
  geom_bar(position="stack", stat="identity") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.key.size = unit(2, 'cm')) +
  facet_grid(CEEffSource~., scales = "free") +
  xlab("CEEffort")
```


## CE official days at sea vs official fishing days {.tabset}


```{r  CEoffEff}

myplotsEff <- list()
for(i in unique(CE$CEArea)){
  myplotsEff[[i]] <- 
    ggplot(subset(CE, CEArea == i), aes(x= CEoffDaySea, y= CEoffFishDay, colour=CEGearActivity)) + geom_point()
}
```

```{r CEoffEffplot, results = "asis"}
for(i in unique(names(myplotsEff))){
    catHeader(names(myplotsEff[i]), 3)
    lapply(myplotsEff[i], print)
}
```

## CE Map

```{r CEMap, fig.dim= c(12, 12)}

world <- ne_countries(scale = "medium", returnclass = "sf")
world <- st_set_crs(world, 4326)

CEMap <- CE %>%
  distinct(CEstatRect) %>%
  mutate(lon = ices.rect(CEstatRect)$lon,
         lat = ices.rect(CEstatRect)$lat)

min.lon<-min(CLMap$lon, na.rm = T)
max.lon<-max(CLMap$lon, na.rm = T)
min.lat<-min(CLMap$lat, na.rm = T)
max.lat<-max(CLMap$lat, na.rm = T)

print(ggplot() +
  theme_bw() +
  geom_sf(data=world)+
  geom_point(data = CEMap, aes(lon, lat), size=2, colour="red") +
               coord_sf(xlim = c(min.lon, max.lon), ylim = c(min.lat, max.lat)) +
               xlab("Longitude") +
               ylab("Latitude"))
```


## CE Potential Errors {.tabset}

### CE ICES rectangles and FAO Areas

Area and ICES rectangle in the CE data (AreaCEtable, RectangleCEtable) set is compared with area/rectangle relationship ICES reference list. 
The expected area related to the ICES rectangle is found in the column ICESAreaWithRectangle.
Note that -9 is allowed as unknown ICES rectangle.

```{r CErectangles}
CERect <- left_join(CE, ICESrect, by = c("CEstatRect" = "ICESNAME"))%>%
  select(CEArea, CEstatRect, Area) %>%
  distinct()

CERectErr <- CERect %>%
  group_by(CEstatRect) %>%
  summarise(CEArea = unique(CEArea),
            Area = paste0(unique(Area), collapse = ", ")) %>%
  rowwise() %>%
  mutate(NoMatch = grepl(CEArea, Area)) %>%
  filter(NoMatch %in% FALSE) %>%
  rename(ICESArea = Area) %>%
  ungroup() %>%
  select(CEstatRect, CEArea, ICESArea) %>%
  rename(RectangleCEtable = CEstatRect,
         AreaCEtable = CEArea,
         ICESAreaWithRectangle = ICESArea)

datatable(CERectErr) 
```

