```{r title, include = F}

front_title <- "RDBES CL Multinational overviews"

```


---
title: `r front_title`
author: "ICES RDBES Core group"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
options(scipen=999)
```

```{r functions, include=FALSE}
catHeader <- function(text = "", level = 3) {
    cat(paste0("\n\n", 
               paste(rep("#", level), collapse = ""), 
               " ", text, "\n"))
}
```

```{r ReadData, echo=FALSE, message=FALSE, warning=FALSE}
#After submission of data call 2021, add check for catchcategory RegDis and logbook registered discard category

library(dplyr)
library(knitr)
library(tidyr)
library(ggplot2)
library(data.table)
library(mapplots)
library(rnaturalearth)
library(rnaturalearthdata)
library(sf)
library(stringr)
library(DT)
library(tidyverse)
library(kableExtra)

setwd("H:/RDBES/QC_CE_CL")

CL <- read.csv("H:\\RDBES\\RDBES CL all data from year 2019\\RDBES CL all data from year 2019.csv",header=T,sep = ",",stringsAsFactors = FALSE)

CL <- CL[CL$CLvesselFlagCountry !='AD' & CL$CLvesselFlagCountry !='',]

CL_DF <- as.data.frame(CL)

CL_DF$n_records <- 1

CL_DF$n_vessels_3[CL_DF$CLnumberOfUniqueVessels<3] <- '<3 vessels'
CL_DF$n_vessels_3[CL_DF$CLnumberOfUniqueVessels>=3] <- '>=3 vessels'
CL_DF$OfficialScientificWeightDiff <- CL_DF$CLofficialWeight - CL_DF$CLscientificWeight

CL_DF_COD <- CL_DF[CL_DF$CLspeciesFaoCode =="COD",]


CL %>% 
group_by(CLstatisticalRectangle, CLvesselFlagCountry) %>% 
summarise(n()) %>% 
ungroup() %>% 
mutate(lon = ices.rect(CLstatisticalRectangle)$lon,
lat = ices.rect(CLstatisticalRectangle)$lat)-> CLmap

world <- ne_countries(scale = "medium", returnclass = "sf")

world <- st_set_crs(world, 4326)

CL_DT <- data.table(CL)

CLsummary <- CL_DT[,.(n=.N), by=.(CLvesselFlagCountry,CLstatisticalRectangle)]
# Get ICES rects centroids
CLsummary[,":="(lon = ices.rect(CLstatisticalRectangle)$lon,
                lat = ices.rect(CLstatisticalRectangle)$lat)]

# Prepare CL maps
CLcountries <- unique(CLsummary$CLvesselFlagCountry)
for(c in CLcountries){
  dataCountry <- CLsummary[CLvesselFlagCountry == c]
  min.lon<-min(dataCountry$lon, na.rm = T)
  max.lon<-max(dataCountry$lon, na.rm = T)
  min.lat<-min(dataCountry$lat, na.rm = T)
  max.lat<-max(dataCountry$lat, na.rm = T)
  d <-
    ggplot() +
    theme_bw() +
    geom_sf(data=world)+
    geom_point(data = dataCountry, aes(lon, lat), size=2, colour="red") +
    coord_sf(xlim = c(min.lon, max.lon), ylim = c(min.lat, max.lat))+
    labs(title = paste0("ICES rectangle centroids in CL data submitted to the RDBES by ",c))
  #assign(d, c)
  ggsave(filename=paste0("H:\\RDBES\\QC_CE_CL\\CL_maps\\CL_",c,"_coords.jpg"), plot=d, height = 12, width = 12)
}


#Read the rectangle list from the repository 
url <- "https://github.com/ices-tools-dev/RDBES/raw/master/QC-scripts/RectangleList/ICESRectAreas.csv"
ICESrect <- read.csv(url, header = TRUE)

```


```{r CLCEcon, include=FALSE}
CL$CLSpecies[CL$CLSpecies==''] <- as.character(CL$CLSpecies)
CL$CLyear <- as.character(CL$CLyear)

# Month factors 
CL$CLmonth <- factor(CL$CLmonth, levels = as.character(c(1:12)))

# Vessel length factors 
CL$CLvesselLengthCategory <- factor(CL$CLvesselLengthCategory, levels = c("<8", "8-<10", "10-<12", "12-<15", "15-<18", "18-<24", "24-<40", "40<", "Unknown"))

```



```{r topMet, include=FALSE}
#Find top 20 CLSpecies
top20_CLSpecies <- CL %>%
  group_by(CLspeciesCode) %>%
  summarise(lvTot=sum(CLtotalOfficialLandingsValue)) %>%
  arrange(desc(lvTot)) %>%
  top_n(20)
top20_CLSpecies$Top20CLSpecies <- "X"
CL1 <- left_join(CL,top20_CLSpecies,by="CLspeciesCode")
CL1$topCLSpecies <- ifelse(is.na(CL1$Top20CLSpecies),"OTH",CL1$CLspeciesCode)

#Find top 20 metiers
top20_metiers <- CL1 %>%
  group_by(CLmetier6) %>%
  summarise(lvTot=sum(CLtotalOfficialLandingsValue)) %>%
  arrange(desc(lvTot)) %>%
  top_n(20)
top20_metiers$Top20metiers <- "X"
CL1 <- left_join(CL1,top20_metiers,by="CLmetier6")
CL1$topMetiers <- ifelse(is.na(CL1$Top20metiers),"OTH",CL1$CLmetier6)

```

Data source: RDBES CL data

##	Overviews number of records by flag countries {.tabset}

### by year

```{r echo=FALSE, message=FALSE, warning = FALSE, fig.height=2}
country_years <- CL_DF %>%
  group_by(CLyear, CLvesselFlagCountry) %>%
  summarise(n_records=sum(n_records)) 

g <- ggplot(country_years, aes(x= CLvesselFlagCountry, n_records))+
  geom_col(aes(fill=CLyear))
g + theme(axis.text.x = element_text(angle=90, hjust=1, size=5))

```

### by CLdataTypeOfScientificWeight

```{r echo=FALSE, message=FALSE, warning = FALSE, fig.height=2}
country_CLdTypSciWeig <- CL_DF %>%
  group_by(CLvesselFlagCountry, CLdataTypeOfScientificWeight) %>%
  summarise(n_records=sum(n_records)) 

g <- ggplot(country_CLdTypSciWeig, aes(x= CLvesselFlagCountry, n_records))+
  geom_col(aes(fill=CLdataTypeOfScientificWeight))
g + theme(axis.text.x = element_text(angle=90, hjust=1, size=5))

```

### by CLdataSourceOfScientificWeight

```{r echo=FALSE, message=FALSE, warning = FALSE, fig.height=2}
country_CLdSouSciWeig <- CL_DF %>%
  group_by(CLvesselFlagCountry, CLdataSourceOfScientificWeight) %>%
  summarise(n_records=sum(n_records)) 

g <- ggplot(country_CLdSouSciWeig, aes(x= CLvesselFlagCountry, n_records))+
  geom_col(aes(fill=CLdataSourceOfScientificWeight))
g + theme(axis.text.x = element_text(angle=90, hjust=1, size=5))

```

### by CLsamplingScheme

```{r echo=FALSE, message=FALSE, warning = FALSE, fig.height=2}
country_CLsampScheme <- CL_DF %>%
  group_by(CLvesselFlagCountry, CLsamplingScheme) %>%
  summarise(n_records=sum(n_records)) 

g <- ggplot(country_CLsampScheme, aes(x= CLvesselFlagCountry, n_records))+
  geom_col(aes(fill=CLsamplingScheme))
g + theme(axis.text.x = element_text(angle=90, hjust=1, size=5))

```

### by CLdataSourceLandingsValue

```{r echo=FALSE, message=FALSE, warning = FALSE, fig.height=2}
country_CLdSouLanVal <- CL_DF %>%
  group_by(CLvesselFlagCountry, CLdataSourceLandingsValue) %>%
  summarise(n_records=sum(n_records)) 

g <- ggplot(country_CLdSouLanVal, aes(x= CLvesselFlagCountry, n_records))+
  geom_col(aes(fill=CLdataSourceLandingsValue))
g + theme(axis.text.x = element_text(angle=90, hjust=1, size=5))

```

### by CLlandingCategory

```{r echo=FALSE, message=FALSE, warning = FALSE, fig.height=2}
country_CLlandCat <- CL_DF %>%
  group_by(CLvesselFlagCountry, CLlandingCategory) %>%
  summarise(n_records=sum(n_records)) 

g <- ggplot(country_CLlandCat, aes(x= CLvesselFlagCountry, n_records))+
  geom_col(aes(fill=CLlandingCategory))
g + theme(axis.text.x = element_text(angle=90, hjust=1, size=5))

```

### by CLcatchCategory

```{r echo=FALSE, message=FALSE, warning = FALSE, fig.height=2}
country_CLcatchCat <- CL_DF %>%
  group_by(CLvesselFlagCountry, CLcatchCategory) %>%
  summarise(n_records=sum(n_records)) 

g <- ggplot(country_CLcatchCat, aes(x= CLvesselFlagCountry, n_records))+
  geom_col(aes(fill=CLcatchCategory))
g + theme(axis.text.x = element_text(angle=90, hjust=1, size=5))

```

### by difference official and scientific weight 

```{r echo=FALSE, message=FALSE, warning = FALSE, fig.height=2}
country_weightdifference <- CL_DF %>%
  group_by(CLvesselFlagCountry, CLexplainDifference) %>%
  summarise(OfficialScientificWeightDiff=sum(OfficialScientificWeightDiff)) 

g <- ggplot(country_weightdifference, aes(x= CLvesselFlagCountry, OfficialScientificWeightDiff))+
  geom_col(aes(fill=CLexplainDifference))
g + theme(axis.text.x = element_text(angle=90, hjust=1, size=5))

```


CL_DF$OfficialScientificWeightDiff


### by CLexplainDifference

```{r echo=FALSE, message=FALSE, warning = FALSE, fig.height=2}
country_CLexplainDifference <- CL_DF %>%
  group_by(CLvesselFlagCountry, CLexplainDifference) %>%
  summarise(n_records=sum(n_records)) 

g <- ggplot(country_CLexplainDifference, aes(x= CLvesselFlagCountry, n_records))+
  geom_col(aes(fill=CLexplainDifference))
g + theme(axis.text.x = element_text(angle=90, hjust=1, size=5))

```

### by number of vessels < 3

```{r echo=FALSE, message=FALSE, warning = FALSE, fig.height=2}
country_CLnVessels3 <- CL_DF %>%
  group_by(CLvesselFlagCountry, n_vessels_3) %>%
  summarise(n_records=sum(n_records)) 

g <- ggplot(country_CLnVessels3, aes(x= CLvesselFlagCountry, n_records))+
  geom_col(aes(fill=n_vessels_3))
g + theme(axis.text.x = element_text(angle=90, hjust=1, size=5))

```

## CL Maps by country{.tabset}
ICES rectangle centroids in CL data submitted to the RDBES


```{r include=FALSE}

world <- ne_countries(scale = "medium", returnclass = "sf")
st_crs(world)
world <- st_set_crs(world, 4326)

```


```{r echo=FALSE, message=FALSE, warning = FALSE}

  min.lon<-min(CLmap$lon, na.rm = T)
  max.lon<-max(CLmap$lon, na.rm = T)
  min.lat<-min(CLmap$lat, na.rm = T)
  max.lat<-max(CLmap$lat, na.rm = T)

countries = sort(unique(CLmap$CLvesselFlagCountry))

countries[1:floor(length(countries)/2)] -> set1

countries[ceiling(length(countries)/2):length(countries)] -> set2


    ggplot() +
    theme_bw() +
    geom_sf(data=world)+
    geom_point(data = CLmap %>% filter(CLvesselFlagCountry %in% set1), aes(lon, lat), size=2, colour="red") +
    facet_wrap(facets = ~CLvesselFlagCountry)+
    coord_sf(xlim = c(min.lon, max.lon), ylim = c(min.lat, max.lat))
    
    
    ggplot() +
    theme_bw() +
    geom_sf(data=world)+
    geom_point(data = CLmap %>% filter(CLvesselFlagCountry %in% set2), aes(lon, lat), size=2, colour="red") +
    facet_wrap(facets = ~CLvesselFlagCountry)+
    coord_sf(xlim = c(min.lon, max.lon), ylim = c(min.lat, max.lat))
```


## CL table (top 20 species (rest grouped in OTH group)) {.tabset}

### CL weight by year and month

```{r CLweightYear, fig.dim= c(12, 8)}
CLweightYear <- CL1 %>%
  group_by(CLyear, CLmonth) %>%
  summarise(CLscientificWeight = sum(CLscientificWeight)) 

ggplot(CLweightYear, aes(CLmonth, CLscientificWeight, fill=CLyear)) +
  geom_bar(position="dodge", stat="identity") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.key.size = unit(2, 'cm'))  +
  xlab("CLMonth") +
  labs(fill = "CLyear")

```


### CL official weight vs scientific weight 

```{r CLoffweightSciweightSP, fig.dim= c(12, 8)}
CLweightS <- CL1 %>%
  group_by(topCLSpecies) %>%
  summarise(CLoffWeight = sum(CLofficialWeight),
            CLsciWeight = sum(CLscientificWeight)) %>%
  gather(CLweightSource, CLweight, -c(topCLSpecies))


ggplot(CLweightS, aes(reorder(topCLSpecies, -CLweight), CLweight, fill = CLweightSource)) +
  geom_bar(position="dodge", stat="identity") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.key.size = unit(2, 'cm'))+
  xlab("topCLSpecies")

```


### CL scientific weight source

```{r CLoffweightSciweightSourceSP, fig.dim= c(12, 8)}
CLweightSource <- CL1 %>%
  group_by(topCLSpecies, CLdataSourceOfScientificWeight) %>%
  summarise(CLsciWeight = sum(CLscientificWeight)) 

ggplot(CLweightSource, aes(reorder(topCLSpecies, -CLsciWeight), CLsciWeight, fill = CLdataSourceOfScientificWeight)) +
  geom_bar(position="stack", stat="identity") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.key.size = unit(2, 'cm')) +
  xlab("topCLSpecies")

```

### CL Landings by area (stacked)

```{r CLLanSArea, , fig.dim= c(12, 8)}
CLLanSArea <- CL1 %>%
  group_by(topCLSpecies, CLarea) %>%
  summarise(CLoffWeight = sum(CLofficialWeight))

CLLanSArea <- CLLanSArea %>%
  group_by(topCLSpecies) %>%
  mutate(TotW = sum(CLoffWeight))

ggplot(CLLanSArea, aes(reorder(topCLSpecies, -TotW), CLoffWeight, fill = CLarea)) +
  geom_bar(position="stack", stat="identity") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  xlab("topCLSpecies")
```


### CL Landings value source 

```{r CLValSSP, fig.dim= c(12, 8)}
CLValS <- CL1 %>%
  group_by(topCLSpecies, CLdataSourceLandingsValue) %>%
  summarise(CLtotalOfficialLandingsValue = sum(CLtotalOfficialLandingsValue)) 

ggplot(CLValS, aes(reorder(topCLSpecies, -CLtotalOfficialLandingsValue), CLtotalOfficialLandingsValue, fill = CLdataSourceLandingsValue)) +
  geom_bar(position="stack", stat="identity") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.key.size = unit(2, 'cm')) +
  xlab("topCLSpecies")
```

### CL Landing category 

```{r CLlandCatSP, fig.dim= c(12, 8)}
CLValS2 <- CL1 %>%
  group_by(topCLSpecies, CLlandingCategory) %>%
  summarise(CLofficialWeight = sum(CLofficialWeight))

ggplot(CLValS2, aes(reorder(topCLSpecies, -CLofficialWeight), CLofficialWeight, fill = CLlandingCategory)) +
  geom_bar(position="stack", stat="identity") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.key.size = unit(2, 'cm')) +
  xlab("topCLSpecies")
```

### CL Catch category 

```{r CLcatchCatSP, fig.dim= c(12, 8)}

CLValS3 <- CL1 %>%
  group_by(topCLSpecies,CLcatchCategory) %>%
  summarise(CLoffWeight = sum(CLofficialWeight))

ggplot(CLValS3, aes(reorder(topCLSpecies, -CLoffWeight), CLoffWeight, fill = CLcatchCategory)) +
  geom_bar(position="stack", stat="identity") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.key.size = unit(2, 'cm')) +
  xlab("topCLSpecies")
```

## CL official weight vs total official landings value {.tabset}

```{r  CLoffWeightValSP}

myplotsVal <- list()
for(i in sort(unique(CL1$topCLSpecies))){
  myplotsVal[[i]] <- 
    ggplot(subset(CL1, topCLSpecies == i), aes(x= CLofficialWeight, y=CLtotalOfficialLandingsValue)) + geom_point()
}
```

```{r CLoffWeightValplotSP, results = "asis"}

for(i in unique(names(myplotsVal))){
    catHeader(names(myplotsVal[i]), 3)
    lapply(myplotsVal[i], print)
}
```



## CL top 20 species maps {.tabset}

```{r  CLMapSP, include=FALSE}

world <- ne_countries(scale = "medium", returnclass = "sf")
world <- st_set_crs(world, 4326)

CLMap <- CL1 %>%
  filter(CLstatisticalRectangle != '-9') %>%
  distinct(CLstatisticalRectangle, topCLSpecies) %>%
  mutate(lon = ices.rect(CLstatisticalRectangle)$lon,
         lat = ices.rect(CLstatisticalRectangle)$lat)
 

myplotsMap <- list()
for(i in sort(unique(CLMap$topCLSpecies))){
  min.lon<-min(CLMap$lon, na.rm = T)
  max.lon<-max(CLMap$lon, na.rm = T)
  min.lat<-min(CLMap$lat, na.rm = T)
  max.lat<-max(CLMap$lat, na.rm = T)
  myplotsMap[[i]] <- 
    ggplot() +
    theme_bw() +
    geom_sf(data=world)+
    geom_point(data = subset(CLMap, topCLSpecies == i), aes(lon, lat), size=2, colour="red") +
    coord_sf(xlim = c(min.lon, max.lon), ylim = c(min.lat, max.lat)) +
    xlab("Longitude") +
    ylab("Latitude")
}
```

```{r CLMapplot, results = "asis", fig.dim = c(12, 12)}

for(i in unique(names(myplotsMap))){
    catHeader(names(myplotsMap[i]), 3)
    lapply(myplotsMap[i], print)
}
```

## CL top 20 metiers (rest grouped in OTH group)) {.tabset}

### CL official weight vs scientific weight 

```{r CLoffweightSciweightME, fig.dim= c(12, 8)}
CLweightS <- CL1 %>%
  group_by(topMetiers) %>%
  summarise(CLoffWeight = sum(CLofficialWeight),
            CLsciWeight = sum(CLscientificWeight)) %>%
  gather(CLweightSource, CLweight, -c(topMetiers))


ggplot(CLweightS, aes(reorder(topMetiers, -CLweight), CLweight, fill = CLweightSource)) +
  geom_bar(position="dodge", stat="identity") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.key.size = unit(2, 'cm')) +
  xlab("topMetiers")

```


### CL scientific weight source

```{r CLoffweightSciweightSourceME, fig.dim= c(12, 8)}
CLweightSource <- CL1 %>%
  group_by(topMetiers, CLdataSourceOfScientificWeight) %>%
  summarise(CLsciWeight = sum(CLofficialWeight)) 

ggplot(CLweightSource, aes(reorder(topMetiers, -CLsciWeight), CLsciWeight, fill = CLdataSourceOfScientificWeight)) +
  geom_bar(position="stack", stat="identity") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.key.size = unit(2, 'cm')) +
  xlab("topMetiers")

```

### CL Landings value source 

```{r CLValSME, fig.dim= c(12, 8)}

CLValS <- CL1 %>%
  group_by(topMetiers, CLarea,CLdataSourceLandingsValue) %>%
  summarise(CLoffValue = sum(CLtotalOfficialLandingsValue))

ggplot(subset(CLValS), aes(reorder(topMetiers, -CLoffValue), CLoffValue, fill = CLdataSourceLandingsValue)) +
  geom_bar(position="stack", stat="identity") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.key.size = unit(2, 'cm')) +
  xlab("topMetiers")

```


## CL top 20 metiers maps {.tabset}

```{r  CLMapME}

world <- ne_countries(scale = "medium", returnclass = "sf")
world <- st_set_crs(world, 4326)

CLMap <- CL1 %>%
  filter(CLstatisticalRectangle != '-9') %>%
  distinct(CLstatisticalRectangle, topMetiers) %>%
  mutate(lon = ices.rect(CLstatisticalRectangle)$lon,
         lat = ices.rect(CLstatisticalRectangle)$lat)
 

myplotsMap <- list()
for(i in sort(unique(CLMap$topMetiers))){
  min.lon<-min(CLMap$lon, na.rm = T)
  max.lon<-max(CLMap$lon, na.rm = T)
  min.lat<-min(CLMap$lat, na.rm = T)
  max.lat<-max(CLMap$lat, na.rm = T)
  myplotsMap[[i]] <- 
    ggplot() +
    theme_bw() +
    geom_sf(data=world)+
    geom_point(data = subset(CLMap, topMetiers == i), aes(lon, lat), size=2, colour="red") +
    coord_sf(xlim = c(min.lon, max.lon), ylim = c(min.lat, max.lat)) +
    xlab("Longitude") +
    ylab("Latitude")
}
```

```{r CLMapplotME, results = "asis", fig.dim = c(12, 12)}

for(i in unique(names(myplotsMap))){
    catHeader(names(myplotsMap[i]), 3)
    lapply(myplotsMap[i], print)
}
```



## Potential Errors {.tabset}

### ICES rectangles and FAO Areas

```{r echo=FALSE, message=FALSE, warning = FALSE}

CLRect <- left_join(CL, ICESrect, by = c("CLstatisticalRectangle" = "ICESNAME"))%>%
  select(CLvesselFlagCountry, CLarea, CLstatisticalRectangle, Area) %>%
  distinct()

CLRectErr <- CLRect %>%
  group_by(CLstatisticalRectangle, CLvesselFlagCountry) %>%
  summarise(CLarea = unique(CLarea),
            Area = paste0(unique(Area), collapse = ", ")) %>%
  rowwise() %>%
  mutate(NoMatch = grepl(CLarea, Area)) %>%
  filter(NoMatch %in% FALSE & CLstatisticalRectangle !='-9') %>%
  rename(ICESArea = Area) %>%
  ungroup() %>%
  select(CLvesselFlagCountry, CLstatisticalRectangle, CLarea, ICESArea) %>%
  rename(RectangleCLtable = CLstatisticalRectangle,
         AreaCLtable = CLarea,
         ICESAreaWithRectangle = ICESArea)

DT::datatable(CLRectErr, filter = 'top')

```
