```{r title, include = F}

front_title <- "RDBES CE Multinational overviews"

```


---
title: `r front_title`
author: "ICES RDBES Core group (MS)"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen=999)
```

```{r ReadData, echo=FALSE, message=FALSE, warning = FALSE}
library(dplyr)
library(knitr)
library(tidyr)
library(ggplot2)
library(data.table)
library(mapplots)
library(rnaturalearth)
library(rnaturalearthdata)
library(sf)
library(stringr)

setwd("D:/Projekty/RDBES/CoreGroup CQ subgroup")

CE <- read.csv("RDBES CE all data from year 2019\\RDBES CE all data from year 2019.csv",header=F,sep = ",",stringsAsFactors = FALSE)
colnames(CE) <- c("CErecType","CEdTypSciEff","CEdSouSciEff","CEnatProgSciEff","CEvesFlagCou","CEyear","CEquar",
                  "CEMonth","CEArea","CEstatRect","CEgsaSubarea","CEjurisdArea","CEeconZoneIndi","CEnatFishAct",
                  "CEmetier6","CEIBmitiDev","CEloc","CEvesLenCat","CEfishTech","CEdeepSeaReg","CEnumFracTrips",
                  "CEnumDomTrip","CEoffDaySea","CESciDaySea","CEoffFishDay","CEsciFishDay","CEoffNumHaulSet",
                  "CEsciNumHaulSet","CEoffVesFishHour","CEsciVesFishHour","CEoffSoakMeterHour","CEsciSoakMeterHour",
                  "CEoffkWDaySea","CEscikWDaySea","CEoffkWFishDay","CEscikWFishDay","CEoffkWFishHour","CEscikWFishHour",
                  "CEgTDaySea","CEgTFishDay","CEgTFishHour","CEnumUniqVes","CEsciFishDayRSE","CEscientificFishingDaysQualBias")

CE <- CE[CE$CEvesFlagCou !='AD' & CE$CEvesFlagCou !='',]

CE_DF <- as.data.frame(CE)


CE_DF$n_records <- 1

CE_DF$n_vessels_3[CE_DF$CEnumUniqVes<3] <- '<3 vessels'
CE_DF$n_vessels_3[CE_DF$CEnumUniqVes>=3] <- '>=3 vessels'
#CL_DF$OfficialScientificWeightDiff <- CL_DF$CLofficialWeight - CL_DF$CLscientificWeight
CE_DF$CEyear <- as.character(CE$CEyear)

# Get gear for passive/active
CE_DF <- mutate(CE_DF, CEGear = str_extract(CEmetier6, "[^_]+"))
CE_DF <- mutate(CE_DF, CEGearActivity = ifelse(CEGear %in% c("FIX", "FAR", "FPN", "FPO", "FWR", "FYK", "GEN", "GNF", "GN", "GNC", "GND", "GNS", "GTN", "GTR", "GES", "LH", "LHM", "LHP", "LL", "LLD", "LLF", "LLS", "LTL", "LVD", "LVS", "LX", "LN", "LNB", "LNP", "LNS","MIS"), "Passive", ifelse(CEGear %in% "NK", "NK", "Active")))


#Read the rectangle list from the repository 
url <- "https://github.com/ices-tools-dev/RDBES/raw/master/QC-scripts/RectangleList/ICESRectAreas.csv"
ICESrect <- read.csv(url, header = TRUE)

```

```{r functions, include = FALSE}
catHeader <- function(text = "", level = 3) {
    cat(paste0("\n\n", 
               paste(rep("#", level), collapse = ""), 
               " ", text, "\n"))
}
```


```{r, include = FALSE}
# Find top 10 metiers accoding to the fishing days
top20_metiers <- CE_DF %>%
  group_by(CEmetier6) %>%
  summarise(ofdTot=sum(CEoffFishDay)) %>%
  arrange(desc(ofdTot)) %>%
  top_n(20)
top20_metiers$Top20metiers <- "X"
CE_DF <- left_join(CE_DF,top20_metiers,by="CEmetier6")
CE_DF$topMetiers <- ifelse(is.na(CE_DF$Top20metiers),"OTH",CE_DF$CEmetier6)

```



Data source: RDBES CE data

## Overviews number of records by flag countries {.tabset}

### by year


```{r echo=FALSE, message=FALSE, warning = FALSE, fig.height=2}
country_years <- CE_DF %>%
  group_by(CEyear, CEvesFlagCou) %>%
  summarise(n_records=sum(n_records)) 

g <- ggplot(country_years, aes(x= CEvesFlagCou, n_records))+
  geom_col(aes(fill=CEyear))
g + theme(axis.text.x = element_text(angle=90, hjust=1, size=5))

```

### by CEdTypSciEff


```{r echo=FALSE, message=FALSE, warning = FALSE, fig.height=2}
country_CEdTypSciEff <- CE_DF %>%
  group_by(CEvesFlagCou, CEdTypSciEff) %>%
  summarise(n_records=sum(n_records)) 

g <- ggplot(country_CEdTypSciEff, aes(x= CEvesFlagCou, n_records))+
  geom_col(aes(fill=CEdTypSciEff))
g + theme(axis.text.x = element_text(angle=90, hjust=1, size=5))


```

### by CEdSouSciEff


```{r echo=FALSE, message=FALSE, warning = FALSE, fig.height=2}
country_CEdSouSciEff <- CE_DF %>%
  group_by(CEvesFlagCou, CEdSouSciEff) %>%
  summarise(n_records=sum(n_records)) 

g <- ggplot(country_CEdSouSciEff, aes(x= CEvesFlagCou, n_records))+
  geom_col(aes(fill=CEdSouSciEff))
g + theme(axis.text.x = element_text(angle=90, hjust=1, size=5))


```

### by CEvesLenCat


```{r echo=FALSE, message=FALSE, warning = FALSE, fig.height=2}
country_CEvesLenCat <- CE_DF %>%
  group_by(CEvesFlagCou, CEvesLenCat) %>%
  summarise(n_records=sum(n_records)) 

g <- ggplot(country_CEvesLenCat, aes(x= CEvesFlagCou, n_records))+
  geom_col(aes(fill=CEvesLenCat))
g + theme(axis.text.x = element_text(angle=90, hjust=1, size=5))


```

### by number of vessels < 3


```{r echo=FALSE, message=FALSE, warning = FALSE, fig.height=2}
country_n_vessels_3 <- CE_DF %>%
  group_by(CEvesFlagCou, n_vessels_3) %>%
  summarise(n_records=sum(n_records)) 

g <- ggplot(country_n_vessels_3, aes(x= CEvesFlagCou, n_records))+
  geom_col(aes(fill=n_vessels_3))
g + theme(axis.text.x = element_text(angle=90, hjust=1, size=5))


```

## Fishing days vs days at sea {.tabset}

### Official fishing days by year and country

```{r echo=FALSE, message=FALSE, warning = FALSE}

CEDASYear <- CE_DF %>%
  group_by(CEyear, CEvesFlagCou) %>%
  summarise(CEoffFishDay = sum(CEoffFishDay)) 

ggplot(CEDASYear, aes(CEvesFlagCou, CEoffFishDay, fill = CEyear)) +
  geom_bar(position="dodge2", stat="identity") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.key.size = unit(2, 'cm'))
```

### Official days at sea by year and country

```{r echo=FALSE, message=FALSE, warning = FALSE}

CEDASYear <- CE_DF %>%
  group_by(CEyear, CEvesFlagCou) %>%
  summarise(CEoffDaySea = sum(CEoffDaySea)) 

ggplot(CEDASYear, aes(CEvesFlagCou, CEoffDaySea, fill = CEyear)) +
  geom_bar(position="dodge2", stat="identity") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.key.size = unit(2, 'cm'))
```

### Official days at sea vs scientific days at sea

```{r CLeffortDATS, fig.dim= c(12, 8), echo = FALSE,  message=FALSE, warning = FALSE}
CEeffortDATS <- CE_DF %>%
  group_by(CEArea) %>%
  summarise(CEoffDaySea = sum(CEoffDaySea),
            CESciDaySea = sum(CESciDaySea))  %>%
  gather(CEDaySeaSource, CEDaySea, -c(CEArea))

ggplot(CEeffortDATS, aes(reorder(CEArea, -CEDaySea), CEDaySea, fill = CEDaySeaSource)) +
  geom_bar(position="dodge", stat="identity") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.key.size = unit(2, 'cm')) +
  xlab("CEDaySea")

```

### Official days at sea and scientific days at sea (passive/active gears) 

```{r CLeffortDATSpa, fig.dim= c(12, 8), echo = FALSE,  message=FALSE, warning = FALSE}
CEeffortDATSpa <- CE_DF %>%
  group_by(CEArea, CEGearActivity) %>%
  summarise(CEoffDaySea = sum(CEoffDaySea),
            CESciDaySea = sum(CESciDaySea))  %>%
  gather(CEDaySeaSource, CEDaySea, -c(CEArea, CEGearActivity))

CEeffortDATSpa <- CEeffortDATSpa %>%
  group_by(CEArea) %>%
  mutate(TotE = sum(CEDaySea))

ggplot(CEeffortDATSpa, aes(reorder(CEArea, -TotE), CEDaySea, fill = CEGearActivity)) +
  geom_bar(position="stack", stat="identity") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.key.size = unit(2, 'cm')) +
  facet_grid(CEDaySeaSource~., scales = "free") +
  xlab("CEFishDay")
```

### Official fishing days vs scientific fishing days 

```{r CLeffortFDS, fig.dim= c(12, 8), echo = FALSE,  message=FALSE, warning = FALSE}
CEeffortFDS <- CE_DF %>%
  group_by(CEArea) %>%
  summarise(CEoffFishDay = sum(CEoffFishDay),
            CEsciFishDay = sum(CEsciFishDay))  %>%
  gather(CEFishDaySource, CEFishDay, -c(CEArea))

ggplot(CEeffortFDS, aes(reorder(CEArea, -CEFishDay), CEFishDay, fill = CEFishDaySource)) +
  geom_bar(position="dodge", stat="identity") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.key.size = unit(2, 'cm')) +
  xlab("CEFishDay")

```


### Official fishing days and scientific fishing days (passive/active gears) 

```{r CLeffortFDSpa, fig.dim= c(12, 8), echo = FALSE,  message=FALSE, warning = FALSE}
CEeffortFDSpa <- CE_DF %>%
  group_by(CEArea, CEGearActivity) %>%
  summarise(CEoffFishDay = sum(CEoffFishDay),
            CEsciFishDay = sum(CEsciFishDay))  %>%
  gather(CEFishDaySource, CEFishDay, -c(CEArea, CEGearActivity))

CEeffortFDSpa <- CEeffortFDSpa %>%
  group_by(CEArea) %>%
  mutate(TotE = sum(CEFishDay))

ggplot(CEeffortFDSpa, aes(reorder(CEArea, -TotE), CEFishDay, fill = CEGearActivity)) +
  geom_bar(position="stack", stat="identity") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.key.size = unit(2, 'cm')) +
  facet_grid(CEFishDaySource~., scales = "free") +
  xlab("CEFishDay")
```

### CE scientific effort source 

```{r CESciEffortSource, fig.dim= c(12, 8), echo = FALSE,  message=FALSE, warning = FALSE}
CESciEffortSource <- CE_DF %>%
  group_by(CEArea, CEdSouSciEff) %>%
  summarise(CESciDaySea = sum(CESciDaySea),
            CEsciFishDay = sum(CEsciFishDay)) %>%
  gather(CEEffSource, CEEffort, -c(CEArea, CEdSouSciEff)) 

ggplot(CESciEffortSource, aes(reorder(CEArea, -CEEffort), CEEffort, fill = CEdSouSciEff)) +
  geom_bar(position="stack", stat="identity") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.key.size = unit(2, 'cm')) +
  facet_grid(CEEffSource~., scales = "free") +
  xlab("CEEffort")
```

## CE official days at sea vs official fishing days {.tabset}


```{r  CEoffEff, echo = FALSE,  message=FALSE, warning = FALSE}

myplotsEff <- list()
for(i in unique(CE_DF$CEArea)){
  myplotsEff[[i]] <- 
    ggplot(subset(CE_DF, CEArea == i), aes(x= CEoffDaySea, y= CEoffFishDay, colour=CEGearActivity)) + geom_point()
}
```


```{r CEoffEffplot, results = "asis", echo = FALSE,  message=FALSE, warning = FALSE}
for(i in unique(names(myplotsEff))){
    catHeader(names(myplotsEff[i]), 3)
    lapply(myplotsEff[i], print)
}
```

## Days at sea vs fishing days by country {.tabset}

### CEoffDaySea vs CEoffFishDay by country

```{r echo=FALSE, message=FALSE, warning = FALSE}

ggplot(CE_DF , aes(x=CEoffDaySea, y=CEoffFishDay)) + 
  geom_point()+
  facet_wrap(~CEvesFlagCou)+
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust=1))

```

### CEosciDaySea vs CEsciFishDay by country

```{r echo=FALSE, message=FALSE, warning = FALSE}

ggplot(CE_DF , aes(x=CESciDaySea, y=CEsciFishDay)) + 
  geom_point()+
  facet_wrap(~CEvesFlagCou)+
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust=1))

```



## CE Maps by country {.tabset}
ICES rectangle centroids in CE data submitted to the RDBES

```{r  mapCE, include = FALSE,  echo=FALSE, message=FALSE, warning = FALSE}
world <- ne_countries(scale = "medium", returnclass = "sf")
world <- st_set_crs(world, 4326)

CE %>% 
distinct(CEstatRect, CEvesFlagCou) %>% 
mutate(lon = ices.rect(CEstatRect)$lon,
       lat = ices.rect(CEstatRect)$lat)-> CEmap

mapCE <- list()
for(i in sort(unique(CEmap$CEvesFlagCou))){
  min.lon<-min(CEmap$lon, na.rm = T)
  max.lon<-max(CEmap$lon, na.rm = T)
  min.lat<-min(CEmap$lat, na.rm = T)
  max.lat<-max(CEmap$lat, na.rm = T)
  mapCE[[i]] <- 
    ggplot() +
    theme_bw() +
    geom_sf(data=world)+
    geom_point(data = subset(CEmap, CEvesFlagCou == i), aes(lon, lat), size=2, colour="red") +
    coord_sf(xlim = c(min.lon, max.lon), ylim = c(min.lat, max.lat)) +
    xlab("Longitude") +
    ylab("Latitude")
}
```

```{r, results = "asis", echo = FALSE, warning = FALSE}

for(i in sort(unique(CEmap$CEvesFlagCou))){
    catHeader(i, 3)
    lapply(mapCE[i], print)
}
```



## Potential Errors {.tabset}


### CE ICES rectangles and FAO Areas

Area and ICES rectangle in the CE data (AreaCEtable, RectangleCEtable) set is compared with area/rectangle relationship ICES reference list. 
The expected area related to the ICES rectangle is found in the column ICESAreaWithRectangle.
Note that -9 is allowed as unknown ICES rectangle.

```{r echo=FALSE, message=FALSE, warning = FALSE}

ICESrect$sq_check <- "correct"

CE_sq <- CE_DF
CE_sq <- CE_sq[CE_sq$CEstatRect != "-9",]
CE_sq$t <- 1

CE_sq1 <- CE_sq %>%
  group_by(CEvesFlagCou, CEstatRect, CEArea) %>%
  summarise(t=sum(t))


CE_sq2 <- CE_sq1 %>% 
  left_join(ICESrect, by= c("CEArea" = "Area", "CEstatRect"="ICESNAME"))

CE_sq3 <- CE_sq2[is.na(CE_sq2$sq_check),]

CE_sq4 <- subset(CE_sq3, select=c(CEvesFlagCou,CEstatRect,CEArea))
DT::datatable(CE_sq4, filter = 'top')

```


### Mandatory fields missing

```{r echo=FALSE, message=FALSE, warning = FALSE}

CE_DF %>% 
  filter(is.na(CEdTypSciEff) | 
           is.na(CEdSouSciEff) | 
           is.na(CEvesFlagCou) |
           is.na(CEyear) |
           is.na(CEquar) |
           is.na(CEArea) |
           is.na(CEstatRect) |
           is.na(CEgsaSubarea) |
           is.na(CEmetier6) |
           is.na(CEIBmitiDev) |
           is.na(CEloc) |
           is.na(CEvesLenCat) |
           is.na(CEnumDomTrip) |
           is.na(CEoffDaySea) |
           is.na(CESciDaySea) |
           is.na(CEoffFishDay) |
           is.na(CEsciFishDay)|
           is.na(CEoffkWDaySea) |
           is.na(CEscikWDaySea) |
           is.na(CEoffkWFishDay) |
           is.na(CEscikWFishDay) |
           is.na(CEgTDaySea) |
           is.na(CEgTFishDay) |
           is.na(CEnumUniqVes)
  ) ->mandatoryMissing

DT::datatable(mandatoryMissing)


```

### GSA subarea missing for area 37


```{r echo=FALSE, message=FALSE, warning = FALSE}

CE_DF %>% 
  filter(grepl('37', CEArea)) %>% 
  filter(is.na(CEgsaSubarea)) -> GSAmissing

DT::datatable(GSAmissing)

```








